Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-11-28 contents/draft.tex
Fix ref label!: re-ranking -> reranking

    The remainder of this paper is organized as follows.
    In Section ~\ref{sec:morphological-analysis-model}, we discuss configuring and training a dictionary-based morphological analysis system.
    In Section ~\ref{sec:re-ranking-model}, we discuss the generation of secondary results of morphological analysis, produce re-ranking data, and propose a method for training a two-stage re-ranking model.
    In Section ~\ref{sec:results}, we discuss the results of the performance improvement using the morphological analysis and re-ranking models.
    In Section ~\ref{sec:related-work}, we introduce previous research cases related to this study.
    Finally, in Section ~\ref{sec:conclusion}, we conclude the study and discuss its limitations and directions for future research.

>>>>

    The remainder of this paper is organized as follows.
    In Section ~\ref{sec:morphological-analysis-model}, we discuss configuring and training a dictionary-based morphological analysis system.
    In Section ~\ref{sec:reranking-model}, we discuss the generation of secondary results of morphological analysis, produce re-ranking data, and propose a method for training a two-stage re-ranking model.
    In Section ~\ref{sec:results}, we discuss the results of the performance improvement using the morphological analysis and re-ranking models.
    In Section ~\ref{sec:related-work}, we introduce previous research cases related to this study.
    Finally, in Section ~\ref{sec:conclusion}, we conclude the study and discuss its limitations and directions for future research.
